Appendix 1: Preregistered analysis with simulated data

### 2025-04-14 preregistration.Rmd
clean table

Items:
<table>
<tr>
<td></td>
<td>Psychological ownership</td>
</tr>
<tr>
<td>
po01 1. I feel a very high degree of personal ownership of donating blood. [Likert]
</td>
</tr>
<td>
po02 2. I feel like donating blood belongs to me. [Likert]
</td> </tr>
<tr>
<td>
po03 3. I feel like I own donating blood. [Likert]
</td> </tr>
<tr> <td></td>

<td>
Self-identity
</td> </tr>
<tr>
<td>
si01 1. Donating blood is important to me. [Likert]
</td> <tr>
si02 2. I am like the kind of person who donates blood. [Likert]
</td> </tr>
<tr> 
<td>
si03 3. Donating blood is an important part of who I am. [Likert]
</td> </tr>
<tr> <td></td>

<td>
Intention
</td></tr>
<tr>
<td>
it01 1. I would like to donate blood in the future. [Likert]
</td>   </tr>
<tr>
<td>
it02 2. I intend to donate blood in the future. [Likert]
</td> </tr>
<tr>
<td>
it03 3. I intend to make more than just a one-off blood donation. [Likert]
</td></tr>
<tr><td></td>
<td>
Intention to donate for emergency
</td></tr>
<tr>
<td>
ie01 1. I would be willing to donate blood if I received an urgent callout from the Finnish Red Cross Blood Service. [Likert]
</td></tr>
<tr><td></td> 
<td>
Antecedents of psychological ownership
</td></tr>
<tr><td></td>

<td>
Control
</td></tr>
<tr>
<td>
ac01  1. I have influence over the things that affect me while donating blood. [Likert]
</td></tr>
<tr>
<td>
ac02 2. I control the location and scheduling for donating blood. [Likert]
</td></tr>
<tr>
<td>
ac03 3. I influence decisions related to my blood donation. [Likert]
</td></tr>
<tr>
<td>
ac04 4. In general, I have control over donating blood. [Likert]
</td></tr>
<tr><td></td>
<td>
Intimate knowledge
</td></tr>
<tr>
<td>
ai01 1. I am intimately familiar with what is going on with regard to donating blood. [Likert]
</td></tr>
<tr>
<td>
ai02 2. I have a depth of knowledge as it relates to donating blood. [Likert]
</td></tr>
<tr>
<td>
ai03 3. I have a comprehensive understanding of donating blood. [Likert]
</td></tr>
<tr>
<td>
ai04 4. I have a broad understanding of donating blood. [Likert]
</td></tr>
<tr><td></td>

<td>
Self-Investment
</td></tr>
<td>
iv01 1.	I have invested a major part of myself into donating blood. [Likert]
</td></tr>
<tr>
<td>
iv02 2. I have invested a significant amount of my time into donating blood. [Likert]
</td></tr>
<tr>
<td>
iv03 3. Overall, I invested a lot into donating blood. [Likert]
</td></tr>
<tr><td></td>

<td>
Blood donation history
</td></tr>
<tr>
<td>
bd01 1. Do you believe that you are currently eligible to donate blood [yes, no, unsure]
</td></tr>
<tr>
<td>
bd02 2. How many times in total have you donated blood at the Finnish Red Cross Blood Service Finland? [select number]
</td></tr>
<tr>
<td>
bd03 3. How many times in the last two years have you donated at the Finnish Red Cross Blood Service? [select number]
</td></tr>
<tr>
<td>
bd04 4. When did you last attend a Finnish Red Cross blood donation centre with the intention of donating blood? [select date]
</td></tr>
<tr><td></td>

<td>
Demographics
</td></tr>
<tr>
<td>
de01 1. What is your gender? [man, woman, non-binary, prefer to not disclose, prefer to self-describe (open response)]
</td></tr>
<tr>
<td>
de02 2. How old are you today? [select number]
</td></tr>
</table>

>>>>

Items:
<table>

<tr>
<td>Psychological ownership</td>
</tr>
<tr>
<td>po01 1. I feel a very high degree of personal ownership of donating blood. [Likert]</td>
</tr>

<tr> 
<td>po02 2. I feel like donating blood belongs to me. [Likert] </td> 
</tr>

<tr>
<td>po03 3. I feel like I own donating blood. [Likert]</td> 
</tr>

<tr> 
<td>Self-identity</td> 
</tr>

<tr>
<td>si01 1. Donating blood is important to me. [Likert]</td> 
<tr>si02 2. I am like the kind of person who donates blood. [Likert]</td> 
</tr>

<tr> 
<td>si03 3. Donating blood is an important part of who I am. [Likert]</td> 
</tr>

<tr>
<td>Intention</td>
</tr>

<tr>
<td>it01 1. I would like to donate blood in the future. [Likert]</td>   
</tr>

<tr>
<td>it02 2. I intend to donate blood in the future. [Likert]</td>
</tr>

<tr>
<td>it03 3. I intend to make more than just a one-off blood donation. [Likert]</td>
</tr>

<tr>
<td>
Intention to donate for emergency</td>
</tr>

<tr>
<td>ie01 1. I would be willing to donate blood if I received an urgent callout from the Finnish Red Cross Blood Service. [Likert]</td>
</tr>

<tr>
<td>Antecedents of psychological ownership</td>
</tr>

<tr>
<td>Control</td>
</tr>

<tr>
<td>ac01  1. I have influence over the things that affect me while donating blood. [Likert]</td>
</tr>

<tr>
<td>ac02 2. I control the location and scheduling for donating blood. [Likert]</td>
</tr>
<tr>

<td>ac03 3. I influence decisions related to my blood donation. [Likert]</td>
</tr>

<tr>
<td>ac04 4. In general, I have control over donating blood. [Likert]</td>
</tr>
<tr>
<td>Intimate knowledge</td>
</tr>

<tr>
<td>ai01 1. I am intimately familiar with what is going on with regard to donating blood. [Likert]</td>
</tr>

<tr>
<td>ai02 2. I have a depth of knowledge as it relates to donating blood. [Likert]</td>
</tr>

<tr>
<td>ai03 3. I have a comprehensive understanding of donating blood. [Likert]</td>
</tr>

<tr>
<td>ai04 4. I have a broad understanding of donating blood. [Likert]</td>
</tr>

<tr>
<td>Self-Investment</td>
</tr>

<tr>
<td>iv01 1.	I have invested a major part of myself into donating blood. [Likert]</td>
</tr>

<tr>
<td>iv02 2. I have invested a significant amount of my time into donating blood. [Likert] </td>
</tr>

<tr>
<td>iv03 3. Overall, I invested a lot into donating blood. [Likert]</td>
</tr>

<tr>
<td>Blood donation history</td>
</tr>

<tr>
<td>bd01 1. Do you believe that you are currently eligible to donate blood [yes, no, unsure]</td>
</tr>

<tr>
<td>bd02 2. How many times in total have you donated blood at the Finnish Red Cross Blood Service Finland? [select number]</td>
</tr>

<tr>
<td>bd03 3. How many times in the last two years have you donated at the Finnish Red Cross Blood Service? [select number]</td>
</tr>

<tr>
<td>bd04 4. When did you last attend a Finnish Red Cross blood donation centre with the intention of donating blood? [select date]</td>
</tr>

<tr>
<td>Demographics</td>
</tr>

<tr>
<td>de01 1. What is your gender? [man, woman, non-binary, prefer to not disclose, prefer to self-describe (open response)]</td>
</tr>

<tr>
<td>de02 2. How old are you today? [select number]</td>
</tr>
</table>
